Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-06 paper/paper.tex
pass

\subsection{Active Recnnaissance}

@@

\Mar{------------------------------- estou aqui}

@@

\Luc{Figure 4 shows a Suricata rule that capture a ping scan performed by the NMAP Tool. The relevant options are in bold---the option \CodeIn{dsize: 0}, indicates that the packet has no bytes in the payload. \CodeIn{itype: 8} identifies the packet as a ICMP Echo request.}

\Luc{To synthesize rules for a Ping Scan, \tname{} analyzes the positive traffic and extract the following set of options:}

\begin{figure}[h]
\vspace{-3ex} \lstinputlisting[language=C,numbers=none,frame=none,keywords={flags,threshold}]{pingscan.suricata.synth}
%  \caption{Suricata rule for SYN Flood Attacks.}
  %  \label{fig:synflood-example-synt}
\vspace{-3ex}  
\end{figure}

\Luc{Again, a rule with this options would capture the positive traffic, but it would be overspecified. So, \tname{} tries to minimize the rule... After the minimization, it produces the following rule:}
\Luc{}

\subsection{\Fix{...some other with contents...}}
\label{sec:content-example}

\Fix{...elaborate...}

@@

>>>>

\subsection{Active Reconnaissance}

@@

@@

Figure 4 shows a Suricata rule that captures a ping scan implemented
with the NMAP Tool~\cite{netmap}. The relevant options are in
bold---the option \CodeIn{dsize: 0} indicates that the packet has no
bytes in the payload and the option \CodeIn{itype: 8} indicates that
the packet to be captured are ICMP Echo requests.

Again, to synthesize rules for a Ping Scan, \tname{} analyzes the
positive traffic and extracts the following rule options:

\begin{figure}[h]
  \vspace{-2ex}
  \lstinputlisting[language=C,numbers=none,frame=none,keywords={dsize,icode,itype}]{pingscan.suricata.synth}
  \vspace{-3ex}  
\end{figure}

Again, note that rule \CodeIn{icode} was not present in the original
rule.  \tname{} produces the following five rules at the top of the
ranking after minimization and ranking.

\Fix{...show rules...}

\subsection{\Fix{Name of attack ***with content***}}
\label{sec:content-example}

\Fix{...please elaborate. We need on example that shows that the
  search can be non-trivial. In the examples above, we had to discard
  only one rule option!}

@@

\Mar{----------------------------------- estou aqui}
